Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-07-10 vesicle_code/docs/adhesion/adhesion.tex
fixed figs 12 and 13

\begin{figure}[htp]
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image01.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image02.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image03.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image04.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image05.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image06.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image07.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image08.png}
  \caption{\label{fig:doublet090-weakAdhesion} The formation of a
  doublet in a shear flow.  The reduced area is $\Delta A = 0.9$, the
  Hamaker constant is $\mathcal{H}=0.7$, the separation distance is
  $\delta = 0.4$, and the shear rate is $\chi=0.5$.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image01.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image02.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image03.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image04.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image05.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image06.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image07.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image08.png}
  \caption{\label{fig:doublet090-strongAdhesion} The formation of a
  doublet in a shear flow.  The reduced area is $\Delta A = 0.9$, the
  Hamaker constant is $\mathcal{H}=2.1$, the separation distance is
  $\delta = 0.4$, and the shear rate is $\chi=0.5$.}
\end{figure}

>>>>

\begin{figure}[htp]
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image01.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image02.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image03.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image04.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image05.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image06.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image07.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image08.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image09.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image10.png}
  \caption{\label{fig:doublet090-weakAdhesion} The formation of a
  doublet in a shear flow.  The reduced area is $\Delta A = 0.9$, the
  Hamaker constant is $\mathcal{H}=0.7$, the separation distance is
  $\delta = 0.4$, and the shear rate is $\chi=0.5$.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image01.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image02.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image03.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image04.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image05.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image06.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image07.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image08.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image09.png}
  \includegraphics[width=0.19\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image10.png}
  \caption{\label{fig:doublet090-strongAdhesion} The formation of a
  doublet in a shear flow.  The reduced area is $\Delta A = 0.9$, the
  Hamaker constant is $\mathcal{H}=2.1$, the separation distance is
  $\delta = 0.4$, and the shear rate is $\chi=0.5$.}
\end{figure}
